---
title: "LBSPR case study: Dolphin fish in Colombia"
subtitle: "Cali workshop - May 26<sup>th</sup>-29<sup>th</sup>, 2025"
author: "Hector Antonio Andrade Rodriguez, Yves Reecht"
institute: 'Institute of Marine Research
  [ <img src="https://www.hi.no/en/hi/resources/layout/HI-logo-farger-engelsk.svg/original" alt="Institute of Marine Research" width="55"/>](https://www.hi.no/en)'
output:
  xaringan::moon_reader:
    css: ["xaringan-themer.css", "theme.css"]
    lib_dir: libs
    nature:
      ratio: '16:9'
      highlightLines: true
      countIncrementalSlides: false
---

<!-- Layout options and styles -->
```{r preamble, include=FALSE, cache=FALSE}
## source(here::here("imr-2023/preamble.R"))
source(file.path(getwd(), "preamble.R"))
do.call(knitr::opts_chunk$set, knitr_opts)
```
<!-- Packages to load -->
```{r libs, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(LBSPR)
```

# Life history and relevance of model assumptions


  * Fast growth (k=) and high natural mortality (M=) => rather typical $M/k \approx 1.5$.

--

  * Early maturation (3-7 months), around 65 cm (55 cm fork-length; estimated using a GLMM).

--

  * In equatorial region, reproduction and growth throughout the year...

  * ...but fishery is seasonal in Colombia (Nov.-Mar.)

--

  **=> Is the equilibrium assumption reasonable?**

--

  Importance to look at how the size composition and estimates vary through the fishing season!

---

# Available data

---

# Data exploration and preparation

---

# LB-SPR 2024-2025

---

## Yearly

---

## Monthly

---

# Uncertainty

---

# Shortcomings

---

# Conclusions




<!-- Local Variables: -->
<!-- coding: utf-8 -->
<!-- ispell-local-dictionary: "english" -->
<!-- fill-column: 100 -->
<!-- End: -->
